Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-05 Paper/paperN.tex
only thing left: conclusion + spell check

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

@@

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occuring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames. This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

%Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]

\section{Discussion}

@@

>>>>

\begin{abstract}
  Information in text can be represented by frames. A frame consists of a predicate with arguments. In this report we discuss two probabilistic latent variable models which are trained by resp. expectation maximization and Gibbs sampling, to induce frames from syntactic tri-grams of the form: verb, subject, object. The latent variable is the frame a verb belongs to. In practice, the models cluster verbs based on the occurrences of arguments they are encountered with. The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters). The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1. 
\end{abstract}

@@

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occuring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames. This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

%Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
\section{Results}
These results are experimental, i.e. the parameters are guessed and therefor probably not optimal. (Since gridsearchis more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
\begin{table}[h]
\begin{tabular}{|l||c|c|}
  \hline
  &dicesim&coherencey\\
  \hline
  \hline
  model 0& 0.28&19\%  \\
  \hline
  model 1&0.29 &71\%  \\
  \hline
\end{tabular}
\caption{results}
\label{results}
\end{table}

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming anotherly &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\label{exframes}
\caption{Frame examples}
\end{table}

\section{Discussion}
As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much. But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are asigned to a frame. It is not clear why this happens, but this are still only experimental results.  Since there are 200 frames it is obvious that the coherency is so low. Other experiments have shown that it is possible to cluster with model 0 though.

The frames in table \ref{exframes} are frames induced by model 1 and are meaningfull in the sense that they consist of clusters of verbs that seem to have a similar meaning. Nontheless, in \textit{harming anotherly} there are verbs which would be better left out. They are assigned this frame though because they occurred in company of the same arguments often. The affection frame is remarkable since these are exactly opposites. This happens in some form in more frames though and can be explained by the fact that verbs with opposite meanings are used with the same arguments, this can be seen as a weakness of the model.

Furthermore auxilary verbs get mostly assigned a complete frame, i.e. they are the only verb assigned to a frame. Other verbs like \textit{(say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find)} also get assigned a complete frame. This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb by nouns it is encountered with, sort of meaningless. This is again a weakness of the model, but could possibly be diminished with more data.

@@

\section*{Who did what}
We all tried to work as much as possible and neccesary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of gridsearch). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody.
